---
title: "Final"
author: "Jiang"
date: "2022-12-12"
output:
  html_document:
    df_print: paged
  pdf_document: default
  always_allow_html: true
---

#### Package

```{r}
library(tidytuesdayR)
library(ggplot2)
library(dplyr)
library(magrittr)
library(tidyr)
library(tidyselect)
library(purrr)
library(tibble)
library(readr)
library(stringr)
#install.packages('janitor')
library(viridis)
library(janitor)
library(DT)
library(kableExtra)
library(tinytex)
#install.packages("webshot")
#webshot::install_phantomjs()
```


```{r}
raw_dat <- tidytuesdayR::tt_load('2022-01-18')
dat <- raw_dat$chocolate
glimpse(dat)
```

#### Data preprocess and Exploratory Data Analysis

```{r}
# Remove "%" sign from cocoa content and convert it to a numeric variable
#convert cocoa_percent to a numeric
chocolate <- dat |>
  mutate(cocoa_percent = str_extract(cocoa_percent, "\\d+") |>
  as.numeric())|>
  mutate(country_of_bean_origin=
           recode(country_of_bean_origin,
                  "Congo"= "Republic of Congo",
                  "DR Congo"= "Democratic Republic of the Congo"))
```

```{r}
chocolate_df<- chocolate |>
   mutate(n_ingredients = str_extract(ingredients, "\\d") |> as.numeric(),
     ingredients_list = str_extract(ingredients, "[A-Za-z,*]+")) |>
  separate_rows(ingredients_list,sep = ",") |>
  mutate(ingredients_list = str_replace_all(ingredients_list,c(
        "^S\\*$" = "sweetener",
        "^S$" = "sugar",
        "C" = "cocoa_butter",
        "V" = "vanilla",
        "B" = "beans",
        "L" = "lecithin",
        "^Sa$" = "salt")),
    ingredients_list = replace_na(ingredients_list, "unknown"),
    flag = 1) |>
  pivot_wider(names_from = ingredients_list,values_from = flag,
              values_fill = 0)
```

#### Company location

```{r}
# Create an object with total number of chocolate counts per company location
Country_Counts <- chocolate |>
  select(company_manufacturer,company_location) |>
  group_by(company_location) |>
  summarise(Count = n()) |>
  arrange(desc(Count)) # Arranges total counts from highest to lowest

# Create table
datatable(Country_Counts, colnames = c("Company Location", "Count"))
```

#### Worldmap of country of bean origin 

```{r}
#summarise by country
chocolate_df2 <- chocolate_df |>
  group_by(country = country_of_bean_origin)|>
  summarise(avg_rating=mean(na.omit(rating)),
            avg_cocoa=mean(na.omit(cocoa_percent)))

#retrieve country geo data
world <- map_data("world2")|>
  filter(region != "Antarctica")

world |>
  merge(chocolate_df2, by.x = "region", by.y = "country", all.x = T) %>%
  arrange(group, order) %>%
  ggplot(aes(x = long, y = lat, group = group, fill = avg_rating)) +
  geom_polygon(color = "white", size = 0.2) +
  scale_fill_viridis("", na.value = "gray90") +
  theme_minimal() +
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank())
ggsave("featured.png")

```

#### most memorable characteristics

```{r}
library(tidytext)

tidy_chocolate <- chocolate_df |>
  unnest_tokens(word, most_memorable_characteristics)

tidy_chocolate |>
  group_by(word) |>
  summarise(n = n(),rating = mean(rating)) |>
  ggplot(aes(n, rating)) +
  geom_hline( yintercept = mean(chocolate$rating), lty = 2,
              color = "gray50", size = 1.5 ) +
  geom_jitter(color = "midnightblue", alpha = 0.7) +
  geom_text(aes(label = word),
    check_overlap = TRUE,
    vjust = "top", hjust = "left",size = 2) +
  scale_x_log10()
```

#### Cocoa content

```{r}
summary(chocolate_df$cocoa_percent)
# Histogram of Cocoa Content
ggplot(data = chocolate_df, aes(x = cocoa_percent)) +
  geom_histogram(bins = 20, alpha = 0.80, color = "dark blue", fill = 'light blue') + 
  theme_light() + 
  coord_cartesian(expand = FALSE, ylim = c(0, 750)) +
  labs(x = "Cocoa Content (%)", 
       y = "Count",
       title = "Distribution of Cocoa Content in Chocolates")
```

#### Rating

```{r}
summary(chocolate_df$rating)
# Histogram of Chocolate Ratings by Cocoa Content
# Create bins of various ranges of cocoa content
chocolate_df$Cocoa.Percent_bin <- cut(chocolate_df$cocoa_percent, 
                                      breaks = c(40, 50, 60, 70, 80, 90,100))
# plot
ggplot(data = chocolate_df, aes(x = rating, fill = Cocoa.Percent_bin)) +
  geom_histogram(bins = 15) +
  theme_light() +
  coord_cartesian(expand = FALSE, ylim = c(0, 700)) +
  scale_fill_brewer(type = "seq", 
                    palette = "YlOrBr", 
                    labels = c("40-50", "50-60", "60-70", "70-80", "80-90", "90-100"), 
                    name = "Cocoa Content (%)") +
  labs(x = "Rating", 
       y = "Count",
       title = "Distribution of Chocolate Ratings")
```

#### Data partitioning

```{r}
library(caret)
#library(matrixStats)
```

```{r}
set.seed(123)
#we use a training data set containing a random sample of 70% of the observation to perform with “Diabetes” as the response and the remains variables as predictors.

partition <- caret::createDataPartition(y = chocolate_df$rating, times = 1, p = 0.7, list = FALSE)

# create training data set
train_set <- chocolate_df[partition,]

# create testing data set, subtracting the rows partition to get remaining 30% of the data
test_set <- chocolate_df[-partition,]
#str(train_set)
#str(test_set)
```

```{r}
X<-train_set[,c(7,12:17,19)]
y <- train_set$rating
x <- data.matrix(X)
```

```{r}
x_test <- data.matrix(test_set[,c(7,12:17,19)])
y_test <- test_set$rating
```

#### RMSE

```{r}
RMSE <- function(true_ratings, predicted_ratings){
    sqrt(mean((true_ratings - predicted_ratings)^2))}
```

#### avg

```{r}
mu <- mean(y, na.rm = TRUE)
mu
naive_rmse <- RMSE(test_set$rating, mu)
naive_rmse
```

#### correlation b/w variables

#### linear model

```{r}
# Determine the correlation between cocoa content and chocolate rating
cor(x = train_set$cocoa_percent, y = train_set$rating, method = "pearson")

#simple plot of rating vs cocoa%
graph <- ggplot(train_set, aes(x = cocoa_percent, y = rating)) +
  geom_point() +
  geom_smooth(method = "lm", col = "light blue")+
  labs(x='Cocoa Percent', y='Rating', title='Linear Regression Plot') +
  theme(plot.title = element_text(hjust=0.5, size=20, face='bold'))+
  theme_minimal()+
  annotate("text", x = 45, y = 1.1, label = "italic(R) ^ 2 == 0.021", parse= TRUE)

graph
```

```{r}
# Fit a linear model to predict rating based on Cocoa Content
mod1 <- lm(rating ~ cocoa_percent, data = train_set)
summary(mod1)

```
```{r}
mod1$coef
y_hat <- mod1$coef[1] + mod1$coef[2]*test_set$cocoa_percent
sqrt(mean((y_hat - test_set$rating)^2))
#rmse = 0.4565
```

#### correlation between rating and cocoa content, as well as other ingredients

```{r}
# Fit a linear model to predict rating based on cocoa content and other ingredients
mod2 <- lm(rating ~
                cocoa_percent+
                sweetener+
                sugar+
                cocoa_butter+
                vanilla+
                beans+
                lecithin+
                salt,
              data=train_set)
summary(mod2)
#stemMod2 <- step(mod2,direction = c("both"))
```

```{r}
library(car)
vif_values <- vif(mod2)
vif_values

df_vif <- data.frame("Model" = c("cocoa_percent", "sweetener","sugar","cocoa_butter","vanilla","beans","lecithin","salt"), 
                 "VIF" = c("1.110422", "12.446042","24.155985","1.231621","1.208095","13.391249","1.264674","1.182485"))
       
kbl(df_vif, booktabs = T) |>
  kable_classic(full_width = T, html_font = "Cambria")
knitr::kable(df_vif, align = "lcc")
```


```{r}

library(corrplot)
cor1 = cor(X)
testRes = cor.mtest(X, conf.level = 0.95)
corrplot(cor1, p.mat = testRes$p, method = 'circle', type = 'lower', insig='blank',
         addCoef.col ='black', number.cex = 0.8, order = 'AOE', diag=FALSE)
```

```{r}
library(glmnet)
mod_ridge <- glmnet(x, y, alpha = 0)
#summary(mod_ridge)
cv_model <- cv.glmnet(x, y, alpha = 0)
best_lambda <- cv_model$lambda.min
best_lambda
plot(cv_model)
best_model <- glmnet(x, y, alpha = 0, lambda = best_lambda)
coef(best_model)
```

```{r}
y_predicted <- predict(mod_ridge, s = best_lambda, newx = x)
sst <- sum((y - mean(y))^2)
sse <- sum((y_predicted - y)^2)
rsq <- 1 - sse/sst
rsq
# 0.07255
summary(mod2)
# R2 = 0.06869 
```

```{r}
test_set$pred_lm <- predict(best_model, x_test)
# Calculate the RMSE of the predictions
test_set |>
  summarize(rmse = RMSE(rating, pred_lm)) |>
  pull(rmse) 
#rmse = 0.4378
```

#### random forest

```{r}
library(randomForest)
set.seed(123)
control <- trainControl(method="cv", number = 5)
grid <- data.frame(mtry = c(1, 5, 10, 25, 50, 100))

train_rf <-  train(x, y, 
                   method = "rf", 
                   ntree = 150,
                   trControl = control,
                   tuneGrid = grid,
                   nSamp = 5000)

fit_rf <- randomForest(x, y, mtry = train_rf$bestTune$mtry)
plot(fit_rf)
```

```{r}
# Create a column called pred to store the prediction from the random forest model
test_set$pred_rf <- predict(fit_rf, x_test)

# Calculate the RMSE of the predictions
test_set |>
  summarize(rmse = RMSE(rating, pred_rf)) |>
  pull(rmse) 
# 0.4331
```

```{r}
importance(fit_rf)
par(mfrow = c(1, 2))
varImpPlot(fit_rf, type = 2, main = "Variable Importance",col = 'black')
plot(fit_rf, main = "Error vs no. of trees grown")
```

#### knn

```{r}
#install.packages("kknn")
library(kknn)
grid1 = expand.grid(.k=seq(10,50, by=2))
control = trainControl(method="cv")
set.seed(123)

fit_knn = train(rating~cocoa_percent+
                sweetener+
                sugar+
                cocoa_butter+
                vanilla+
                beans+
                lecithin+
                salt, data=train_set, method="knn", 
                trControl=control, tuneGrid=grid1,na.action = na.omit)
fit_knn
ggplot(fit_knn, highlight = TRUE)#k = 18
```

```{r}
test_set$pred_knn <- predict(fit_knn, x_test)

# Calculate the RMSE of the predictions
test_set |>
  summarize(rmse = RMSE(rating, pred_knn)) |>
  pull(rmse) 
#0.4399
```

#### RMSE result

```{r}
df <- data.frame("Model" = c("Just The Average","Simple Linear Regression", "Multivariable Regression","Random Forest Model","K-Nearest Neighbors Model"), 
                 "RMSE" = c("0.4611","0.4565", "0.4378","0.4331","0.4399")) 
kbl(df, booktabs = T) |>
  kable_classic(full_width = T, html_font = "Cambria")
knitr::kable(df, align = "lcc")
```

\newpage

# Appendix: All code for this report

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```
